Histograms

### 2021-07-02 analysis/histograms.Rmd
feat: add MELD histograms

>>>>

# MELD Scores (imputed)

```{r histograms_meld, results = "asis", message = FALSE, warning = FALSE}
meldv <- c(paste0("ScoreMeld", c("", "Unos", "Na", "NaUnos")), "ProbMeldPlus7")
for (v in meldv) {
    cat("\n\n##", v , "\n\n")
    .hist(zlog_data[[v]], main = paste0("Histogram of ", v), xlab = v)
    .qqnorm(zlog_data[[v]], yname = v)
}
```
